Step 10: Pool Results Across PS Methods Using Rubin's Rules

### 2025-09-08 reanalysis-10-pooling_results.qmd
ps save bug

  # Create the plot
  forest_plot <- ggplot(forest_data, aes(x = reorder(method_label, or), y = or)) +
    geom_pointrange(aes(ymin = lower, ymax = upper, color = color), size = 0.8) +
    geom_point(aes(color = color), size = 3) +
    geom_text(aes(label = sprintf("%.2f", or), color = color), 
              vjust = -1.2, hjust = 0.5, size = 4) +
    coord_flip() +
    scale_color_identity() +
    scale_y_continuous(breaks = seq(0.5, max(forest_data$upper, 1.5), by = 0.1),
                       trans = "log",
                       labels = function(x) sprintf("%.1f", x)) +
    scale_x_discrete(expand = c(0.075, 0.075)) +
    theme_minimal(base_size = 14) +
    labs(
      x = element_blank(),
      y = "Odds Ratio",
      title = "Propensity Score Method Comparison",
      subtitle = "Pooled estimates across multiple imputations using mice package (Rubin's rules)",
      caption = "All methods use ATT (Average Treatment Effect in the Treated) estimand"
    ) +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold", margin = margin(b = 10)),
      plot.subtitle = element_text(hjust = 0.5, margin = margin(b = 15)),
      legend.position = "none",
      axis.line = element_line(color = "gray80"),
      axis.text = element_text(color = "gray30"),
      axis.ticks = element_line(color = "gray80"),
      axis.title.x = element_text(margin = margin(t = 10)),
      plot.caption = element_text(margin = margin(t = 15), hjust = 0),
      plot.margin = margin(20, 20, 30, 20)
    ) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "gray70")

>>>>

  # Create the plot
  forest_plot <- ggplot(forest_data, aes(x = reorder(method_label, or), y = or)) +
    geom_pointrange(aes(ymin = lower, ymax = upper, color = color), size = 0.8) +
    geom_point(aes(color = color), size = 3) +
    geom_text(aes(label = sprintf("%.2f", or), color = color), 
              vjust = -1.2, hjust = 0.5, size = 4) +
    coord_flip() +
    scale_color_identity() +
    scale_y_continuous(breaks = seq(0.5, max(forest_data$upper, 1.5), by = 0.1),
                       trans = "log",
                       labels = function(x) sprintf("%.1f", x)) +
    scale_x_discrete(expand = c(0.075, 0.075)) +
    theme_minimal(base_size = 14) +
    labs(
      x = element_blank(),
      y = "Odds Ratio",
      title = "Propensity Score Method Comparison",
      subtitle = "Pooled estimates across multiple imputations using mice package (Rubin's rules)",
      caption = "All methods use ATT (Average Treatment Effect in the Treated) estimand"
    ) +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold", margin = ggplot2::margin(b = 10)),
      plot.subtitle = element_text(hjust = 0.5, margin = ggplot2::margin(b = 15)),
      legend.position = "none",
      axis.line = element_line(color = "gray80"),
      axis.text = element_text(color = "gray30"),
      axis.ticks = element_line(color = "gray80"),
      axis.title.x = element_text(margin = ggplot2::margin(t = 10)),
      plot.caption = element_text(margin = ggplot2::margin(t = 15), hjust = 0),
      plot.margin = ggplot2::margin(20, 20, 30, 20)
    ) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "gray70")
